Next Trippy Structures\thanks{Supported by organization x.}

### 2019-01-16 paper.tex
Extract explained

 \caption{Obtaining the codes of the journeys from the line \l that should arrive to the stop \s within the time range given by \ta and \tz}
\end{algorithm}

@@

\begin{figure}[hbt!]
\includegraphics[width=\textwidth]{example_trips.eps}
\caption{An example of five trips represented on \ctr~(with the optimizations for (ii) and (iii))}
\label{fig:example_ctr}
\end{figure}

@@

 \caption{Querying for all features on \ctr where \DataSty{CSA}, \DataSty{WML} and \DataSty{WMJ} are structures (i), (ii) and (iii), respectively}
\end{algorithm}

>>>>

 \caption{Obtaining the codes of the journeys from the line \l that should arrive to the stop \s within the time range given by \ta and \tz}
 \label{alg:jcodes}
\end{algorithm}

@@

\begin{figure}[hbt!]
\includegraphics[width=\textwidth]{example_trips.eps}
\caption{An example of five trips represented on \ctr with the optimizations for (ii) and (iii)}
\label{fig:example_ctr}
\end{figure}

As \ctr is a complete representation of the collection of trips, we are able to extract any trip using the structures described. \marginpar{The idea here is that explaining how to extract will help understand the more complex FromXtoY query later} The algorithm to extract a trip is shown in the Algorithm~\ref{alg:extract}, where \FuncSty{Rank} and \FuncSty{Select} operate over the bitvector $D$ from (i), \FuncSty{WML}{($s_a$)} is the WM corresponding to the stop \DataSty{$s_a$} in the optimized version of (ii) and \FuncSty{TrackDown} returns the leaf index of a WM given a root index. In a practical implementation, it is not needed to access (ii) and (iii) for the line identifier and jcode of the last stop of the trip, as they will always match the ones from the previous ones.

\begin{algorithm}[hbt!]
\SetKwData{la}{$l_a$}\SetKwData{lz}{$l_z$}\SetKwData{sa}{s$_a$}\SetKwData{sz}{s$_z$}\SetKwData{ta}{t$_a$}\SetKwData{tz}{t$_z$}\SetKwData{pattern}{pattern}\SetKwData{left}{left}\SetKwData{right}{right}\SetKwData{csa}{CSA}\SetKwData{wmj}{WMJ}\SetKwData{leftzero}{left$_0$}\SetKwData{rightzero}{right$_0$}\SetKwData{a}{a}\SetKwData{z}{z}\SetKwData{ja}{j$_a$}\SetKwData{jz}{j$_z$}\SetKwData{n}{n}\SetKwData{ap}{a'}\SetKwData{zp}{z'}\SetKwData{offset}{offset}\SetKwData{i}{i}\SetKwData{trip}{trip}
 \SetKwFunction{GetRange}{GetRange}\SetKwFunction{GetJCodes}{GetJCodes}\SetKwFunction{GetCount}{GetCount}\SetKwFunction{GetPsi}{$\Psi$}\SetKwFunction{GetRangeSpecial}{GetRange$^*$}\SetKwFunction{wml}{WML}\SetKwFunction{TrackUp}{TrackUp}\SetKwFunction{Select}{Select}\SetKwFunction{fxy}{FromXtoY\_full}\SetKwFunction{extract}{Extract\_trip}\SetKwFunction{access}{Access}\SetKwFunction{rank}{Rank}\SetKwFunction{TrackDown}{TrackDown}
 \SetKwProg{Fn}{Function}{\string:}{}

 \Fn{\extract{\i}}{
 \KwData{trip number \i}
 \KwResult{Sequence of tuples $<s,l,j>$ that compose the trip}
 \BlankLine
 \trip $\leftarrow$ []\;
 \a  $\leftarrow$ \GetPsi{\csa, \i}\;
 \sa $\leftarrow$ \rank{\csa,\a}\;
 \BlankLine
 \While{\sa $\neq$ 0}{
    \z $\leftarrow$ \Select{\csa,\sa}\;
    \la $\leftarrow$ \access{\wml{\sa}, \a-\z}\;
    \ja $\leftarrow$ \access{\wmj, \TrackDown{\wml{\sa}, \a-\z}+\z}\;
    append $<\sa,\la,\ja>$ to \trip\;
    \a  $\leftarrow$ \GetPsi{\csa, \i}\;
    \sa $\leftarrow$ \rank{\csa,\a}\;
 }
 \BlankLine
 \Return{\trip}\;
 }

 \caption{Extracting the trip \DataSty{i} from \ctr where \FuncSty{CSA}, \FuncSty{WML} and \FuncSty{WMJ} are structures (i), (ii) and (iii), respectively}
 \label{alg:extract}
\end{algorithm}

@@

 \caption{Querying for all features on \ctr where \FuncSty{CSA}, \FuncSty{WML} and \FuncSty{WMJ} are structures (i), (ii) and (iii), respectively}
 \label{alg:xy}
\end{algorithm}
